\documentclass{article}

    %the math packages
    \usepackage{amsmath,amsfonts,amssymb,amsthm}
    \theoremstyle{plain}
    \newtheorem{thm}{Theorem}[section]
    \newtheorem{lem}[thm]{Lemma}
    \newtheorem{prop}[thm]{Proposition}
    \newtheorem*{cor}{Corollary}
    
    \theoremstyle{definition}
    \newtheorem{defn}{Definition}[section]
    \newtheorem{conj}{Conjecture}[section]
    \newtheorem{exmp}{Example}[section]
    
    \theoremstyle{remark}
    \newtheorem*{rem}{Remark}
    \newtheorem*{note}{Note}
    
    \usepackage{mathtools}
    \usepackage{optidef}
    %add new math packages here
    
    %--------------------------
    
    
    %the algorithm packages
    \usepackage{algorithm}
    \usepackage{algorithmicx}
    \usepackage{algpseudocode}
    \algrenewcommand\algorithmicrequire{\textbf{Input:}}
    \algrenewcommand\algorithmicensure{\textbf{Output:}}
    %add new algorithm packages here
    
    %-------------------------------
    
    \usepackage{graphicx}
    \usepackage{tikz}
    \usepackage{subfigure}
    
    % In case you need to adjust margins:
    \topmargin=-0.45in      %
    \evensidemargin=0in     %
    \oddsidemargin=0in      %
    \textwidth=6.5in        %
    \textheight=9.0in       %
    \headsep=0.25in         %
    
    %newcommand for the format of the homework
    \newcommand{\Answer}{\ \\\textbf{Answer:} }
    \newcommand{\Acknowledgement}[1]{\ \\{\bf Acknowledgement:} #1}
    
    \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
    %end the newcommand for this part
    
    %new command for the partial derivatives
    \newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
    \newcommand{\spd}[3]{\frac{\partial^2 #1}{\partial #2 \partial #3}}
    \newcommand{\grad}[1]{\nabla #1}
    \newcommand{\curl}[1]{\nabla \times #1}
    \newcommand{\dive}[1]{\nabla \cdot #1}
    %end the new command for this part
    
    \title{\bf\huge Network Science Project Report}
    \author{Haoyu Zhao,2016012390}
    \date{}
    
    \begin{document}
    \maketitle

    \begin{abstract}

    \end{abstract}

    \section{Introduction}
    \subsection{Introduction to the Problem}

    \subsection{Related Works}

    \subsection{Basic Settings and Problem Formulation}

    \subsection{Hardness of the Problem}
    \subsubsection{Exploration vs. Exploitation}

    \subsubsection{Exponential Number of Arms}

    \section{Methods to Solve the Problem}
    \subsection{General Methods}
    To tackle the problem of the unknown distribution of the edges, we apply the framework in multi-arm bandit. However, in the network information syncronization setting, the number of possible result will be exponentially large with respect to the number of nodes. Fortunately, \cite{chen2013combinatorial} gave a framework of combinatorial multi-armed bandit to deal with the problem of exponentially number of `arms'. We apply the framework, and the algorithm in that framework, and combine it with the network information synchronization problem. The algorithm is shown in \textbf{Algorithm \ref{cucb}}

    \begin{algorithm}
        \caption{Algorithm to solve the online information syncronization problem}
        \label{cucb}
        \begin{algorithmic}[1]
        \Require The graph structure(without weight) $G(V,E)$, and the algorithm $\mathcal A$ we want to run online.
        \Ensure The action of each round
        \Procedure{Alg}{$G(V,E),\mathcal A$}
            \State $\hat \mu_i \leftarrow$ the empirical expectation of edge $i$.
            \State $T_i \leftarrow$ the number of time the edge $i$ is used.
            \State Every time we use an edge $i$, we will update the empirical expectation $\hat \mu_i$ and the counter $T_i$.
            \For{$t = 1,2,\dots,|E|$}
                \State Play an instance from all possible instances which contains the egde $i$.
            \EndFor
            \For{$t=|E|+1,\dots$}
                \State $\bar\mu_i \leftarrow \hat\mu_i - \sqrt{\frac{3\ln t}{2T_i}}$.
                \State Play an instance which minimize the result of algorithm $\mathcal A$ when each edge has weight $\bar\mu_i$.
            \EndFor
        \EndProcedure
        \end{algorithmic}
    \end{algorithm}

    \subsection{Minimize the Total Cost}
    In this section, we consider the setting when we want to minimize the cost of information synchronization in the network. Now suppose that the random variable $X_i$ on edge $i$ represents the cost of select edge $i$. In this setting, we just consider the total cost but not consider the other measurements. This setting is reasonable in many real life cases when the information synchronization does not have constraints on time but the cost of communication is large, especially when the information synchronization does not happen so often and the cost of synchronization is high. We have the following simple theorem under this setting, and we assume that the random variables that represent the cost on each edge are positive.\\

    \begin{thm}\label{min-spanning-tree}
        Under the senerio of minimizing the total cost while synchronizing the information, the edges that are chosen by the optimal strategy will form a spanning tree.
    \end{thm}
    \begin{proof}
        This theorem is really simple. First because we want to synchronize the information for all nodes, the chosen edges will let all of the nodes to be connected. Then because all of the edges have positive cost, then if there is a cycle it must be non-optimal. So the optimal strategy will choose a spanning tree of the graph.
    \end{proof}

    Now it is obvious that the best strategy tries to find the minimum expectation cost spanning tree, which is the spanning tree that minimize the total cost in the long term. We have the following algorithm, see \textbf{Algorithm \ref{cucbmintree}}, which follows the framework \textbf{Algorithm \ref{cucb}}.

    \begin{algorithm}
        \caption{Algorithm to solve the problem under the min cost setting}
        \label{cucbmintree}
        \begin{algorithmic}[1]
        \Require The graph structure(without weight) $G(V,E)$.
        \Ensure The action of each round, where the edge selected in each round forms a spanning tree of all the nodes and then the algorithm tries to minimize the long term total cost of the spanning tree.
        \Procedure{Alg}{$G(V,E)$}
            \State $\hat \mu_i \leftarrow$ the empirical expectation of edge $i$.
            \State $T_i \leftarrow$ the number of time the edge $i$ is used.
            \State Every time we use an edge $i$, we will update the empirical expectation $\hat \mu_i$ and the counter $T_i$.
            \For{$t = 1,2,\dots,|E|$}
                \State Find an arbitrary spanning tree that contains edge $t$.
            \EndFor
            \For{$t=|E|+1,\dots$}
                \State $\bar\mu_i \leftarrow \hat\mu_i - \sqrt{\frac{3\ln t}{2T_i}}$.
                \State Find the minimum spanning tree with $\bar\mu_i$ as the weight on edge $i$.
            \EndFor
        \EndProcedure
        \end{algorithmic}
    \end{algorithm}

    Now the only problem is how to find the minimum spanning tree of a graph. The problem is simple and we can use Kruskal's algorithm. Then given a spanning tree of the graph, we can transfer the information through the edges of the tree and we can synchronize the infromation.

    \subsection{Minimize the Maximum Distance}
    In this subsection, we consider the case when we want to minimize the time when we synchronize all the information. Here we assume that the weight of each edge $e = (u,v)$ represent the time that information goes from $u$ to $v$ or $v$ to $u$.

    \subsubsection{A very simple case}
    Now we start from a simple case of our problem, we add an assumption about our problem.\\
    
    \textbf{Assumption 1:} The cost of each edge is a constant, and we know the constant.\\
    
    Under this setting, the fastest way to complete the information synchronization is that $\forall u,v\in V$, $u$ send the information to $v$ through the shortest path between $u,v$ and $v$ send the information to $u$ along the shortest path from $v$ to $u$. However, finding the union of the shortest path of all pair of points usually has $O(n^2)$ edges, and it is very wasting if every edge just transfer little information.\\

    Here we use another method to transfer the information, and we need the following definition.

    \begin{defn}\label{center}
        (Center) Given a graph $G(V,E)$, we call a vertex $v\in V$ the center of graph $G$, such that
        \[v = \arg\min_{u\in V}\{\max_{u'\in V}\text{dist}(u,u')\},\]
        where $\text{dist}(u,u')$ denotes the shortest distance from $u$ to $u'$.
    \end{defn}

    Now given $G(V,E)$, denote $v\in V$ as the center of graph $G$, then denote $T$ as the shortest path tree rooted at $v$. The shortest path tree only has $|V|-1$ edges so it is really saving when we no not have so much cost. Moreover, we have the following theorem which shows that given the center and the shortest path tree rooted at the center, the strategy is not so bad.

    \begin{thm}
        If $v\in V$ is the center of graph $G(V,E)$ and $T$ is the shortest path tree of $G$ rooted at $v$, then consider the following strategy, all of the node transfer it's own information to $v$ through tree $T$, and after collecting all the information, the node $v$ transfer all of the information to each nodes. Then this strategy is a $2$ approximation with respect to the time, i.e. it cost at most twice the time of the optimal strategy.
    \end{thm}

    \begin{proof}
        The proof is really simple. Denote $d = \min_{u\in V}\{\max_{u'\in V}\text{dist}(u,u')\}$, which is the maximum distance from the center $v$ to any other nodes. Then denote $d' = \max_{u,u'}\text{dist}(u,u')$, there $\text{dist}$ denote the shortest path length between $u,u'$. Then we know that $d$ is the time required by our strategy, and $d'$ is the time required by the optimal strategy. Then we have
        \[d' = \text{dist}(u,u') \le \text{dist}(u,v) + \text{dist}(v,u') \le d + d = 2d.\]
    \end{proof}

    Now given the theorem, we know that if we can find the center of the graph and then figure out the shortest path tree rooted at the center, then the solution is a good approximation of the optimal solution, and the number of edges is minimized.\\

    Now the only problem is how to find the center and the shortest path tree. First we call the `All Pair Shortest Path' algorithm to find the shortest distance between every $2$ nodes, and we denote the distance matrix $D$, such that $d_{ij} = \text{dist}(v_i,v_j)$. Then we find $c = \arg\min_{i}\max_j d_{ij}$, then $c$ is the center of the graph. At last we call the shortest path algorithm to find the shortest path tree rooted at $c$.\\

    We know that `All Pair Shortest Path' problem can be solved in $O(n^3)$ by the Floyd algorithm, and the shortest path tree can be found by Dijkstra algorithm, and the total running time is $O(n^3)$.

    \subsubsection{A not so simple case}
    Now we consider a not so simple case, which we have the assumption that the each random variable is a constant but we do not know the constant. Then our solution is to call the algorithm framework (\textbf{Algorithm \ref{cucb}}), and turned it into the online version, see \textbf{Algorithm \ref{cucbcentertree}}.

    \begin{algorithm}
        \caption{Algorithm to solve the problem under the min time setting}
        \label{cucbcentertree}
        \begin{algorithmic}[1]
        \Require The graph structure(without weight) $G(V,E)$.
        \Ensure The action of each round, where the edge selected in each round forms a spanning tree of all the nodes and then the algorithm tries to find the minimize the information transfer time in the long term.
        \Procedure{Alg}{$G(V,E)$}
            \State $\hat \mu_i \leftarrow$ the empirical expectation of edge $i$.
            \State $T_i \leftarrow$ the number of time the edge $i$ is used.
            \State Every time we use an edge $i$, we will update the empirical expectation $\hat \mu_i$ and the counter $T_i$.
            \For{$t = 1,2,\dots,|E|$}
                \State Find an arbitrary spanning tree that contains edge $t$.
            \EndFor
            \For{$t=|E|+1,\dots$}
                \State $\bar\mu_i \leftarrow \hat\mu_i - \sqrt{\frac{3\ln t}{2T_i}}$.
                \State Find the center of the graph $G$ and the corresponding shortest path tree rooted at the center with $\bar\mu_i$ as the weight on edge $i$.
            \EndFor
        \EndProcedure
        \end{algorithmic}
    \end{algorithm}


    \subsubsection{Another not so simple case}
    Now we consider the case that the distribution of each random variable on the edge is known. Similar as the previous discussion, we also want to find a `center' of the graph and a spanning tree rooted at the center, such that the spanning tree minimize the largest distance from the center we choose. Formally, we want to find a spanning tree $T$ rooted at $v$ such that
    \[\mathbb E[\max_{u,T}\text{dist}(v,u)],\]
    is minimized, where the distance function $\text{dist}$ denote the shortest path from $v$ to $u$ on the tree $T$.\\

    Note that computing the exact spanning tree that minimize the objective function may be difficult, and we try an approximate solution. We compute the mean weight of each edge and we find the center and the corresponding shortest path tree rooted at the center with respect to the mean of each weight. Our solution is approximate because of the following fact of the objective functions,
    \[\mathbb E[\max_{u,T}\text{dist}(v,u)] \ge \max_{u,T}\mathbb E[\text{dist}(v,u)],\]
    since the max function is convex. Then the algorithm is the same as the most simple case, given the mean of each edge.

    \subsubsection{The general case}
    Then in the general case, we do not know the distribution of the random variables. We also use the approximate solution as shown in the previous case. Then combined with the online settings, we can thus reuse the algorithm when the random variables are constants, see \textbf{Algorithm \ref{cucbcentertree}}.

    \section{Simulation}
    \subsection{Minimize the Total Cost}

    \subsection{Minimize the Maximum Distance}
    \subsubsection{The case when the time is constant but unknown}

    \subsubsection{The general case}

    \subsection{Analysis and Further Discussion}

    \section{Conclusion}

    \newpage
    \bibliographystyle{ieeetr}
    \bibliography{mybib}

    
    \end{document}
    